\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-10-24 document/XSGRB_sample.tex
Adding ABBA and ADC

X-shooter can cover the spectral wavelength region from 3000 \AA~to 24800 \AA~in
a single exposure, by splitting the light in three separate spectroscopic arms
using dichroics. This way each arm work as a separate instrument, each
functioning as its own echelle spectrograph. The ultraviolet blue(UVB) arm
covering 3000 - 5500 \AA, the visual(VIS) arm covering 5500 - 10200 \AA, and the
near-infrared()NIR) arm covering 10200 - 24800 \AA~ with the possibility of
applying a k-band blocking filter cutting the coverage of the NIR arm at 10200 -
21000 \AA.
\\

\todo{ABBA}

For the large majority of the bursts we have observed with a slit width of
1\farc0, 0\farc9, and 0\farc9 for the UVB, VIS, and NIR-arm respectively, which
puts a lower limit on the delivered resolution of the spectra based on the
tabulated values of the delivered resolutions, which is 4350, 7450, and 5300 for
the UVB, VIS and NIR-arm respectively\footnote{\url{https://www.eso.org/sci/facilities/paranal/instruments/xshooter/inst.html}}.
The slit width also sets the width of the atmospheric sky lines and determines
the amount of light lost due to the wavelength-dependent seeing PSF extending
outside the coverage of the slit, where the width of sky-lines is always set by
the slit width whereas both the delivered resolution and the slitloss changes
for the better as the seeing PSF drops below the slit width.
For atmospheric conditions delivering a seeing PSF with a FWHM of 0\farc9
observed with a 0\farc9 slit only 76.1 percent of the light will enter the slit,
meaning that for almost all observations a slitloss correction is required. We
describe how slitlosses were corrected for in Sect. \ref{postproc}.
For accurate measurements of velocity widths, a precise instrumental resolution
is required and this becomes better when the delivered seeing is better than the
slit width. We discuss this in Sect. \ref{resolution}.
\\
\todo{ADC discussion}

@@

%A fraction of the bursts presented here \todo{Insert exact
%number} have already had their hosts investigated in \citet{Kruhler2015}, for
%which extractions of the hosts exist. The focus of the data presented here are
%on the afterglows themselves and in the absence of a clear afterglow, the host.
%We will not, however, investigate the hosts.

>>>>

X-shooter can cover the spectral wavelength region from 3000 \AA~to 24800 \AA~in
a single exposure, by splitting the light in three separate spectroscopic arms
using dichroics. This way each arm work as a separate instrument, each
functioning as its own echelle spectrograph. The ultraviolet blue(UVB) arm
covering 3000 - 5500 \AA, the visual(VIS) arm covering 5500 - 10200 \AA, and the
near-infrared()NIR) arm covering 10200 - 24800 \AA~ with the possibility of
applying a k-band blocking filter cutting the coverage of the NIR arm at 10200 -
21000 \AA. For all observations, a nod-and-shuffle observing scheme has been
employed, with a nodding throw of 5 \arcsec. The individual observations has
been carried out in a standard ABBA pattern, which allows flexibility in the sky
subtraction method for the different arms.

For the large majority of the bursts we have observed with a slit width of
1\farc0, 0\farc9, and 0\farc9 for the UVB, VIS, and NIR-arm respectively, which
puts a lower limit on the delivered resolution of the spectra based on the
tabulated values of the delivered resolutions, which is 4350, 7450, and 5300 for
the UVB, VIS and NIR-arm respectively\footnote{\url{https://www.eso.org/sci/facilities/paranal/instruments/xshooter/inst.html}}.
The slit width also sets the width of the atmospheric sky lines and determines
the amount of light lost due to the wavelength-dependent seeing PSF extending
outside the coverage of the slit, where the width of sky-lines is always set by
the slit width whereas both the delivered resolution and the slitloss changes
for the better as the seeing PSF drops below the slit width.
For atmospheric conditions delivering a seeing PSF with a FWHM of 0\farc9
observed with a 0\farc9 slit only 76.1 percent of the light will enter the slit,
meaning that for almost all observations a slitloss correction is required. We
describe how slitlosses were corrected for in Sect. \ref{postproc}.
For accurate measurements of velocity widths, a precise instrumental resolution
is required and this becomes better when the delivered seeing is better than the
slit width. We discuss this in Sect. \ref{resolution}.

Due to mechanical issues, the atmospheric dispersion corrector (ADC) were
disabled from 1st of August 2012. No bursts were affected by the failing ADC
prior to disablement. To avoid chromatic slit losses due to atmospheric
dispersion, all subsequent observations have been carried out at parallactic
angle. A consequence of this is that for all observations following 1st of
August 2012, the source moves across the spatial direction of the slit as a
function of wavelength. This effect has been modeled in the extraction
procedure, as described in \ref{extract}.

@@

A subset of the bursts presented here  have already had their hosts investigated
in \citet{Kruhler2015}, for which extractions of the hosts exist. The focus of
the data presented here are on the afterglows themselves and in the absence of a
clear afterglow, the host. We will not, however, investigate the hosts.
